---
title: "Property_Property_GLODAP"
author: "Ann McNichol"
date: "12/5/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load Libraries and data sets
```{r}
library(tidyverse)
library(here)

glo_dat <- read_csv(here("data/glodap_dic.csv"))
nos_glo_dat <- read_csv(here("data/nosams_glodap.csv"))
```
Plot d13C vs PO4 for full GLODAP data set
```{r}
ggplot(glo_dat, aes(phosphate, c13, color = depth)) +
  geom_point()
```
Plot d13C vs PO4 for GLODAP deeper than 2000 m; depth
```{r}
glo_dat %>% 
  filter(depth > 2000) %>%
  ggplot(aes(phosphate, c13, color = depth)) +
  geom_point()
```
Ditto; latitude
```{r}
glo_dat %>% 
  filter(depth > 2000) %>%
  ggplot(aes(phosphate, c13, color = latitude)) +
  geom_point()
```
Ditto; longitude
```{r}
glo_dat %>% 
  filter(depth > 2000) %>%
  ggplot(aes(phosphate, c13, color = longitude)) +
  geom_point()
```
Plot d13C vs PO4 for NOSAMS data in GLODAP deeper than 2000 m; longitude
```{r}
nos_glo_dat %>% 
  filter(depth > 2000) %>%
  ggplot(aes(phosphate, c13, color = longitude.x)) +
  geom_point()
```
Ditto: depth
```{r}
nos_glo_dat %>% 
  filter(depth > 2000) %>%
  ggplot(aes(aou, c13, color = depth)) +
  geom_point()
```

```{r}
nos_glo_dat %>%
  filter(depth < 2000) %>%
  ggplot(aes(c14, c13, color = depth)) +
  geom_point()
```

```{r}
nos_glo_dat %>%
  filter(depth > 2000) %>%
  ggplot(aes(c14, c13, color = depth)) +
  geom_point()
```

```{}

library(sf)
library(nngeo)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)


# set ggplot theme
theme_set(theme_bw())
```

Map it.

```{}
# Make it spatial
glodap_sp <- as.data.frame(glodap) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326 )

# Aaand let's take a look
world <- ne_countries(scale = "medium", returnclass = "sf")
ggplot(data = world) +
  geom_sf(data = glodap_sp, size = .1) +
  geom_sf()