---
title: "NOSAMS_secondaries"
author: "Ann McNichol"
date: "12/18/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load libraries and data

```{r}
library(tidyverse)
library(here)

nosams <- read_csv(here("data/ann_jul_17_QA_R.csv"))

```

# boxplot of 13C data for secondaries


```{r}
fill <- "#4271AE"
line <- "#1F3552"

d13C_box <- ggplot(nosams, aes(x = as.factor(RN2), y = d13C_1)) +
  geom_boxplot(fill = fill, color = line) +
  scale_x_discrete(name = "Receipt Number") +
  scale_y_continuous(name = "d13C, o/oo", breaks = seq(-1.0,1.5, 0.25), limits = c(-1.0, 1.5)) +
  ggtitle("Boxplot of median DI13C for NOSAMS secondary standards") +
  theme_bw() + 
  geom_jitter(alpha = 0.4, size = 0.2)
d13C_box
```

#now to figure out how to extract the statistics

```{r}
fill <- "#4271AE"
line <- "#1F3552"

d13C_box_stats <- boxplot(d13C_1 ~ RN2, data = nosams) 
d13C_box_stats

```

#calculate mean and stdev for each RN; also select and look at weird results

```{r}
nosams %>% 
  group_by(RN2) %>%
  summarize(avg = mean(d13C_1, na.rm = TRUE), stand = sd(d13C_1, na.rm=TRUE), num = n())


nosams %>%
  filter(RN2 == 2) %>%
  select(RN2, d13C_1)
```

#generate and save data in csv file

<<<<<<< HEAD
The code below is very flawed. Check out the later version that works, thank you Sam!


nosams %>% 
  group_by(RN2) %>%
   d13C_stats <- summarize(, avg = mean(d13C_1, na.rm = TRUE), stand = sd(d13C_1, na.rm=TRUE), num = n()) 

  write.csv(d13C_stats, file = "d13C_stats.csv")


#boxplot for DI14C results

```{r}

fill <- "#4271AE"
line <- "#1F3552"

D14C_box <- ggplot(nosams, aes(x = as.factor(RN2), y = D14C)) +
  geom_boxplot(fill = fill, color = line) +
  scale_x_discrete(name = "Receipt Number") +
  scale_y_continuous(name = "D14C, o/oo") +
  ggtitle("Boxplot of median DI14C for NOSAMS secondary standards") +
  theme_bw() + 
  geom_jitter(alpha = 0.4, size = 0.2)
D14C_box
```

```{r}
d13C_stats <- nosams %>% 
  group_by(RN2)
  
d13C_stats_sumary <- summarize(d13C_stats, avg = mean(d13C_1, na.rm = TRUE), stand = sd(d13C_1, na.rm=TRUE), num = n()) 

  write.csv(d13C_stats, file = "d13C_stats.csv")
=======
```{r}
nosams_sum <- nosams %>% 
  group_by(RN2) %>%
  summarize(avg = mean(d13C_1, na.rm = TRUE), 
            stand = sd(d13C_1, na.rm=TRUE), 
            num = n())

write_csv(nosams_sum, here("data/secondarysum.csv"))
>>>>>>> 31c34e50a4e5d472e6bd22c13ca5615bc1289b1b
```

