---
title: "NOSAMS-GLODAP join"
author: "Brett Longworth"
date: "7/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Joining the GLODAP and NOSAMS data now takes place in joinNOSAMSGLODAP.R. This file is now primarily for investigating the joined data and making sure the join makes sense.


```{r}
library(tidyverse)
library(lubridate)
library(here)
library(skimr)
library(amstools)
library(odbc)
```


```{r}
# Load glodap
dic_colspec <- cols(
  cruise = col_integer(),
  station = col_integer(),
  cast = col_integer(),
  collection_time = col_datetime(format = ""),
  latitude = col_double(),
  longitude = col_double(),
  bottomdepth = col_double(),
  maxsampdepth = col_double(),
  bottle = col_integer(),
  pressure = col_double(),
  depth = col_double(),
  temperature = col_double(),
  theta = col_double(),
  salinity = col_double(),
  oxygen = col_double(),
  aou = col_double(),
  phosphate = col_double(),
  tco2 = col_double(),
  talk = col_double(),
  c13 = col_double(),
  c13f = col_integer(),
  c14 = col_double(),
  c14f = col_integer(),
  c14err = col_double(),
  expocode = col_character()
)

glodap_dic <- read_csv(here("data/glodap_dic.csv"), col_types = dic_colspec, na = c("NA", "-9999") )
problems(glodap_dic)
skim(glodap_dic)
```
```{r}
# load nosams
nosams_dic <- read_csv(here("data/nosams_clivar.csv"))
skim(nosams_dic)
```

Using a left join to retain all nosams, but we're missing a fair amount of data from GLODAP. Why?

```{r}
joined_dic <- read_csv(here("data/nosams_glodap.csv"))
skim(joined_dic)
```

Let's troubleshoot. Find the unique expocodes from both datasets and see where they overlap and where they don't.

```{r}
filter(joined_dic, bottle > 90)
filter(joined_dic, f_modern < 0.1)
```

```{r}
# expocodes in glodap
glodap_expo <- unique(glodap_dic$expocode)
# nosams expocodes
nosams_expo <- unique(nosams_dic$expocode)
# glodap expocodes in nosams, after conversion from NOSAMS codes
nosams_glo_expo <- unique(nosams_dic$glodap)

# expocodes in both datasets
intersect(glodap_expo, nosams_glo_expo) %>% sort()
```

Expocodes in NOSAMS that aren't in GLODAP

```{r}
setdiff(nosams_glo_expo, glodap_expo) %>% sort()
```

Mostly really recent, so that makes sense.


Expocodes in GLODAP that aren't in NOSAMS 

```{r}
setdiff(glodap_expo, nosams_glo_expo) %>% sort()
```

Compare this to expocodes in GLODAP that don't match any (converted) NOSAMS expocodes in our DB.

```{r}
# expocodes in db
con <- conNOSAMS()
nos_exp_db <- dbGetQuery(con, "SELECT DISTINCT expocode FROM woce_loc")
nrow(nos_exp_db)

setdiff(glodap_expo, nosams_glo_expo) %>% sort()
```

## Create an expocode conversion file

OK, it's clear nosams expocodes are fubar. Let's make a conversion table and edit it manually...

No need to run this. Already done.

```{}
nosams_glodap_exp <- setdiff(nosams_expo, glodap_expo) %>% 
  sort() %>% 
  cbind("nosams" = ., "glodap" = "") %>% 
  as_tibble()

write_csv(nosams_glodap_exp, here("data/nosams_glodap_exp.csv"))
```

```{}
# format this into a tibble
nos_exp_db <- nos_exp_db %>%
  mutate(nosams = trimws(expocode)) %>%
  select(nosams) %>%
  cbind(., "glodap" = "") %>% 
  as_tibble()

# current conversion file
nos_glo_exp <- read_csv(here("doc/nosams_glodap_exp.csv"))

# add this to the previously created conversion file.
nos_glo_exp_full <- rbind(nos_glo_exp, nos_exp_db) %>% 
  distinct(nosams, .keep_all = TRUE) %>% 
  arrange(nosams)

write_csv(nos_glo_exp_full, here("doc/nosams_glodap_exp.csv"))
```

# Plots

```{r}
ggplot(joined_dic, aes(collection_date, f_modern)) +
  geom_point() +
  xlim(as.Date(c('1972-01-01', '2020-01-01'), format="%Y-%m-%d") ) +
  ggtitle("Measurements in NOSAMS")

ggplot(glodap_dic, aes(as.Date(collection_time), c14)) +
  geom_point() +
  xlim(as.Date(c('1972-01-01', '2020-01-01'), format="%Y-%m-%d") ) +
  ggtitle("Measurements in GLODAP")

ggplot(joined_dic, aes(collection_date, c14)) +
  geom_point() +
  xlim(as.Date(c('1972-01-01', '2020-01-01'), format="%Y-%m-%d") ) +
  ggtitle("GLODAP measurements also in NOSAMS")

ggplot(joined_dic, aes(collection_date, (d14c(f_modern, year(collection_date)) - c14))) + 
  geom_point() +
  xlim(as.Date(c('1972-01-01', '2020-01-01'), format="%Y-%m-%d") ) +
  ggtitle("Measurements in NOSAMS and GLODAP (difference)",
          subtitle = "Can't calc d14C if no collection year")
```


