---
title: "Hydrographic Station Reoccupations"
output:
  html_document:
    df_print: paged
---

Find nearby stations that sample the same spot over time.

```{r}
library(here)
library(sf)
library(nngeo)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(tidyverse)

# set ggplot theme
theme_set(theme_bw())
```

Load data. Working with GLODAP initially. 

```{r}
glodap <- read_csv(here("data/glodap_dic.csv"))

# Make it spatial
glodap_sp <- as.data.frame(glodap) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326 )

# Aaand let's take a look
world <- ne_countries(scale = "medium", returnclass = "sf")
ggplot(data = world) +
  geom_sf(data = glodap_sp, size = .1) +
  geom_sf()
```

Find distances to neighbor stations, 

```{r}
# First just use top sample of every station
glodap_stations <- glodap_sp %>%
  group_by(expocode, station) %>%
  slice(which.min(depth))

# Another way to do the same (first is quicker)
#glodap_stations <- glodap_sp %>%
#  group_by(expocode, station) %>%
#  filter(rank(depth, ties.method="first")==1)

# Find nearest stations
nearest_stations <- st_nn(glodap_stations, glodap_stations, 
                          returnDist = T, k = 5, 
                          maxdist = 50000, progress = TRUE)

str(nearest_stations)

write_rds(nearest_stations, here("data/nearest_stations.rds"))
```

OK, we've got a list that has 1. A list of stations by row in glodap_stations, each with a list of the 5 nearest stations. 2. A matrix of stations with the distances to the 5 nearest. 

Problems: 
Closest station is always itself with a distance of 0. =P Fix this one by dropping the station from the list to compute nn's or drop the first element in the result.

Most common closest stations are nearby stations on the same cruise. Fix by only finding distances to stations on different cruises. This still has the problem of finding multiple stations from the same cruise as the closest to a given station.

OK, let's try just parsing out the identity and same cruise stations from the initial spatial join. We can also try and remove multiple nearest stations from the same subsequent cruise. We'll need more nearest entries to make this work properly.

```{r}
# Drop self matches
neighbor_stations <- nearest_stations$nn %>% 
  discard(~ length(.x) == 1) %>%
  flatten_int() %>%
  unique() %>%
  sort()

# returns vector of stations without stations not on the same cruise as row index
clst <- function(row) {
  nearest_stations$nn[[row]][glodap_stations[row,]$cruise != glodap_stations[nearest_stations$nn[[row]],]$cruise]
}

neighbor_stations2 <- map(seq_along(nearest_stations$nn), clst) %>%
  flatten_int() %>%
  unique() %>%
  sort()

# Looks like we're doing OK with this
setdiff(neighbor_stations, neighbor_stations2)

# Use this to select rows that have nearby neighbors
glodap_nearby_stations <- glodap_stations[c(neighbor_stations2),]

# Plot all stations that are close to other stations
ggplot(data = world) +
  geom_sf(data = glodap_nearby_stations, aes(color = expocode), size = .5) +
  geom_sf() +
  theme(legend.position = "none") 

# zoom in
ggplot(data = world) +
  geom_sf(data = glodap_nearby_stations, aes(color = expocode), size = .5) +
  geom_sf() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(-104, -102), ylim = c(-16, -18), expand = FALSE)

# Works, except we're still capturing nearest stations from the same cruise.
# Maybe we can map() keep() to check whether the nearby stations for each station are from the same year or cruise
```


Investigate a couple of specific locations

```{r}
nearest_stations$nn[[188]]

nn <- glodap_stations[c(188, 2635),]
nn <- glodap_stations[nearest_stations$nn[[433]],]
# filter rows for full matching stations from glodap data
# Plot profiles for these stations
# join all these little data sets and plot globally to pick interesting overlap points
nn
# Plot
ggplot(data = world) +
  geom_sf(data = nn, aes(color = expocode), size = 1) +
  geom_sf() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(-80, -70), ylim = c(-30, -40), expand = FALSE)

# generalize
getnearest <- function(station) {
  glodap_stations[c(station, all_nearest[[station]]$nn[[1]][[1]]),]
}
```


### Unused code

If we do these before using st_nn(), we'll have to run a separate st_nn() for every station. This also has problems with indexing due to the list of stations to find distance to is different for every station.

```{}
# Same, also not including stns from same cruise. Only have to not do same cruise because identity is part of the same cruise. Duh. 
nearest_st <- st_nn(glodap_stations[1,], 
                          glodap_stations[glodap_stations$cruise != glodap_stations$cruise[1],],
                          returnDist = T, k = 5, maxdist = 50000, progress = TRUE)

# Generalize as a function for all stations

nn_stations <- function(station) {
  st_nn(glodap_stations[station,], 
        glodap_stations[glodap_stations$cruise !=
                        glodap_stations$cruise[station],],
        returnDist = T, k = 5, maxdist = 50000, progress = TRUE)
}

nn_stations(188)

# We want this, but need to figure out how to extract what we need
all_nearest <- lapply(c(1:nrow(glodap_stations)), nn_stations)

# write it so we don't have to do it again.
save(all_nearest, file = here("data/all_nearest_stations.RData"))


str(all_nearest, max.level = 1)
str(all_nearest[[49]]$nn)
```

Now parse this list of lists of lists and vectors.

```{}
# list of nearest stations for one station
all_nearest[[49]]

# pick the nearest
all_nearest[[49]]$nn[[1]][[1]]


# Let's get stn 49's closest station, extract the data and plot
# This doesn't work
glo49 <- slice(glodap_stations, 49)
glo49

# This does
glo49 <- glodap_stations[c(49, 1554),]

# Plot
ggplot(data = world) +
  geom_sf(data = glo49, size = 2) +
  geom_sf() +
  coord_sf(xlim = c(-70, -60), ylim = c(-60, -50), expand = FALSE)

# generalize
getnearest <- function(station) {
  glodap_stations[c(station, all_nearest[[station]]$nn[[1]][[1]]),]
}

getnearest(188)

# Plot. Uh oh.
ggplot(data = world) +
  geom_sf(data = glo49, size = 2) +
  geom_sf() 
```
